### 2021-07-11 doc/thesis/chapters/implementation.tex
adapt
matlab transmitter

Fig.\ref{fig:bd_dsp_detailed} displays the detailed DSP chain as a block diagram. The following list explains implementation details about the respective DSP blocks.

\includepicture [1.0] [0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/draw.io/bd_dsp_detailed}

\begin{itemize}
  \item \textbf{Data Source}\\
      Matlab is used to generate the data source file, which is used as an input to the system.
      An audio file is read and modulated as an FM channel signal.

@@

@@

\subsection{Transmitter block diagram}

>>>>

Fig.\ref{fig:bd_dsp_detailed} displays the detailed DSP chain as a block diagram.

\includepicture [1.02] [0] [H] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/draw.io/bd_dsp_detailed}

The following list explains implementation details about the respective DSP blocks.
\begin{itemize}
  \item \textbf{Data Source}\\
      Matlab is used to generate the data source file, which is used as an input to the system.
      An audio file is read and modulated as an FM channel signal.

@@

Matlab is used to create a model of the receiver, which is used as a reference for the other implementation variants.
Here, DSP algorithms are tested and evaluated, to find a method that is suitable to implement in hardware, specifically in an FPGA.

The Matlab script consists of a transmitter, the receiver model, and additional code for analysis.

\subsection{Transmitter}

The transmitter is implemented to provide a reproducable source of data, which can be used to feed the receiver.
Another option would be to use external hardware as a software-defined radio and record some antenna data.
However, the main advantage of a locally implemented transmitter over a recording is, that the raw data input is known.
Thus, the expected output of the receiver model is this raw data, that was previously modulated by the local transmitter.
In the case of a recording, the original data is not known, which does not allow to actually verify the receiver.\\

In the implemented version, an audio file is modulated into the FM channel.
The audio file contains data that represents speech with the words \textit{'Left channel... Right channel...'}.
In terms of audio channels, the words exactly match the respective channels' output - the first part is modulated on the left audio channel only, while the second part only targets the right audio channel.
This is particulary useful for verification, especially to verify the functionality of channel separation.
From the experience during development, the channel separation is a good indicator of whether the system is functioning correctly.
This left-right indication also simplifies the verification process, because a developer can recognize it with their visual and acoustic senses.
It is possible to audibly verify it by listening to the output.
It is also possible to just visually inspect the the output data, where a clear separation is visible.

A block diagram of the transmitter structure is depicted in Fig.\ref{fig:bd_matlab_transmitter}.

\includepicture [1.0] [0] [H] {Block diagram of the implemented transmitter in Matlab.} {bd_matlab_transmitter} {img/draw.io/bd_matlab_transmitter}

@@
